Assessing the impacts of time to detection distribution assumptions on detection probability estimation

### 2017-05-18 ReviewerComments.tex
Fix typo

As the authors’ suggest, most point-count studies are designed to maximize availability, which is typically high for birds (e.g., 80-95\%) with perceptibility (e.g., the probability an observer detects a cue that is given by an animal) being the much larger source of bias.  Therefore, this model, without including a supplemental method to estimate perceptibility, is of limited use to many readers.
\begin{quote}
We agree.
This manuscript applies to removal-only analyses.
Still, the concept can be carried over to removal-distance analyses, as we describe in a paragraph of the Discussion.
The implementation will be more complicated and will vary depending on how removal- and distance-sampling are integrated.
This is ongoing work for us.
\end{quote}
Further, although the method may be more accurate even for constant detection data, the loss in precision is such that users will likely not opt to use it unless they suspect non-constant detection through time.  Further, given its presumably arduous computation times (albeit unknown), adding a perceptibility component to the model would likely greatly increase computational demands with unknown implications to bias and precision.  Including a paragraph in the Discussion that outlines when the model would be most beneficial to users (e.g., what type of data, surveys, or sample sizes) and explicitly stating drawbacks (e.g., computation time, loss of precision) would greatly improve this section.  
\begin{quote}
We have attempted to address these comments in the discussion:
``If the estimation of abundance is the primary interest, 
then the choice of TTDD has large consequences ... we would be skeptical of 
abundance estimates that indicate a nonpeaked TTDD with median posterior 
estimates of $\pdet$ below 0.75 ...
An assumption of constant detection limits the shape of $\ftdt$ and 
thereby constrains uncertainty but at the cost of potentially sizable bias...
all found constant-detection models to be flawed, 
producing underestimates of abundance and too-narrow error estimates; 
these resulted in inadequate coverage and also overstatement of effect 
significance.''

>>>>

As the authors’ suggest, most point-count studies are designed to maximize availability, which is typically high for birds (e.g., 80-95\%) with perceptibility (e.g., the probability an observer detects a cue that is given by an animal) being the much larger source of bias.  Therefore, this model, without including a supplemental method to estimate perceptibility, is of limited use to many readers.
\begin{quote}
We agree.
This manuscript applies to removal-only analyses.
Still, the concept can be carried over to removal-distance analyses, as we describe in a paragraph of the Discussion.
The implementation will be more complicated and will vary depending on how removal- and distance-sampling are integrated.
This is ongoing work for us.
\end{quote}
Further, although the method may be more accurate even for constant detection data, the loss in precision is such that users will likely not opt to use it unless they suspect non-constant detection through time.  Further, given its presumably arduous computation times (albeit unknown), adding a perceptibility component to the model would likely greatly increase computational demands with unknown implications to bias and precision.  Including a paragraph in the Discussion that outlines when the model would be most beneficial to users (e.g., what type of data, surveys, or sample sizes) and explicitly stating drawbacks (e.g., computation time, loss of precision) would greatly improve this section.  
\begin{quote}
We have addressed these comments in the discussion:
``If the estimation of abundance is the primary interest, 
then the choice of TTDD has large consequences ... we would be skeptical of 
abundance estimates that indicate a nonpeaked TTDD with median posterior 
estimates of $\pdet$ below 0.75 ...
An assumption of constant detection limits the shape of $\ftdt$ and 
thereby constrains uncertainty but at the cost of potentially sizable bias...
all found constant-detection models to be flawed, 
producing underestimates of abundance and too-narrow error estimates; 
these resulted in inadequate coverage and also overstatement of effect 
significance.''
